%----------------------------------------------------------------------------------------
%  PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.4in,top=0.3in,right=0.4in,bottom=0.3in]{geometry} % Document margins
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[hidelinks]{hyperref}

\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}

\name{Yuqi HAN}
\address{Apt.\ 76-10-04, R\'esidence Schaeffer, B\^atiment 76, Palaiseau 91120, France}
\address{+33 07 86 64 28 70 \ \textbar\  \href{mailto:yuqihan2001@163.com}{yuqihan2001@163.com}}

\begin{document}

%----------------------------------------------------------------------------------------
%  EDUCATION SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Education}

{\bf \'Ecole Polytechnique} \hfill {Sep 2023 -- Present}\\
MScT in Energy Technology and Management \hfill Palaiseau, France\\
GPA: 3.78/4.00\\
Leave of Absence (Gap Year): Sep 2024 -- Jun 2025 (Academic Year 2024--2025)\\
Major Courses: Wind Energy; GHG Emissions; Energy Modelling; Optimization; Environmental Economics; Decision Theory (Energy Systems)

{\bf Exchange and Visiting Programs} \hfill {}\\
France--Swiss Mobility Exchange Research Student (Confirmed) \hfill {Mar 2026 -- Sep 2026}\\
\textbf{\'Ecole Polytechnique F\'ed\'erale de Lausanne (EPFL)} \hfill Switzerland\\
EuroTeQ Exchange Student (Confirmed) --- \textit{Sustainable Cities Student Challenge} (Hybrid) \hfill {Feb 2026 -- Jul 2026}\\
\textbf{Technical University of Munich (TUM)} \hfill Germany

{\bf Northwestern Polytechnical University} \hfill {Sep 2019 -- Jun 2023}\\
Bachelor of Engineering in Flight Vehicle Propulsion Engineering \hfill Xi'an, China\\
GPA: 83.6/100\\
Major Courses: Renewable Energy and Hybrid Power; Thermodynamics; Engineering Fluid Mechanics; Aerodynamics

\end{rSection}

%----------------------------------------------------------------------------------------
%  TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Skills and Interests}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{4ex}} p{0.78\textwidth} }
Interests &
Energy System Optimization; Hydrogen Value Chains; Power-to-X; Sustainable Energy Systems Integration; Low-carbon Transition; Net-Zero Pathways. \\

Tools &
AutoCAD (Basic); CATIA V5; ANSYS Fluent; SolidWorks; Python; AMPL; MATLAB; Simulink. \\
\end{tabular}

\end{rSection}

%-------------------------------------------------------------------------------
%  PROJECTS
%-------------------------------------------------------------------------------
\begin{rSection}{Projects}

\begin{rSubsection}{The Role of Refineries in Future European Energy Systems (Tentative)}{Mar 2026 -- Sep 2026}{Planned Research Internship}{EPFL Valais, Switzerland}
\item[] \textit{Supervised by: Prof.\ Dr.\ Fran\c{c}ois Mar\'echal (Industrial Process and Energy Systems Engineering Laboratory, \'Ecole Polytechnique F\'ed\'erale de Lausanne (EPFL)) and Yi Zhao (PhD student).}
\item Conduct a comprehensive literature review on refinery transition pathways under deep decarbonization.
\item Develop MILP and multi-objective optimization models in \textbf{AMPL} to analyze refinery evolution options.
\item Optimize the integration of refineries into future European energy systems using \textbf{EnergyScope}.
\item Compare alternative transition pathways and prepare clear model documentation and a final internship report (EPFL--TotalEnergies collaboration).
\end{rSubsection}

\begin{rSubsection}{Techno-economic Analysis and Optimization of Sustainable Aviation Fuel (SAF) Refineries}{Apr 2024 -- Sep 2024}{Research Intern}{\'Electricit\'e de France (EDF)}
\item[] \textit{Supervised by: Bruno P\'echin\'e (\'Electricit\'e de France) and Prof.\ Dr.\ Beno\^it Gabrielle (Universit\'e Paris-Saclay).}
\item \textbf{Optimization Framework Formulation:} Formulated a mathematical optimization framework incorporating temporal and regional variations in biomass feedstock and green hydrogen costs.
\item \textbf{Technology Pathway Modeling:} Modeled multiple equipment configurations and reaction pathways for SAF production to enable comprehensive comparative assessment.
\item \textbf{MILP Application \& Route Identification:} Applied mixed-integer linear programming (MILP) to analyze techno-economic trade-offs and identify the most profitable technology routes and optimal geographic deployment.
\item \textbf{Strategy \& Profitability Quantification:} Determined the optimal production strategy and quantified project-level profitability under varying market and regional conditions.
\item \textbf{Project Outcome:} Delivered a comprehensive techno-economic feasibility report for project partners (EDF, Axens, China Environmental Protection Group) to provide strategic investment guidance.
\end{rSubsection}

\begin{rSubsection}{Numerical Simulation Study on Premixed Hydrogen-Enriched Natural Gas Combustion}{Oct 2022 -- Jun 2023}{Student Thesis}{Shaanxi Provincial Key Laboratory of Thermal Science in Aero Power Systems}
\item[] \textit{Supervised by: Prof.\ Dr.\ Hongxia Liang.}
\item \textbf{Geometry \& Meshing:} Built a single-tube combustor geometry in \textbf{SolidWorks} and generated computational meshes for \textbf{ANSYS Fluent}; verified grid independence based on temperature and species/emission outputs.
\item \textbf{Premixed Reacting-Flow CFD (k--$\varepsilon$ + EDC):} Set up premixed combustion simulations in \textbf{ANSYS Fluent} using the \textbf{k--$\varepsilon$} turbulence model coupled with the \textbf{Eddy Dissipation Concept (EDC)}; maintained a fixed equivalence ratio across all cases for consistent comparison.
\item \textbf{Hydrogen Blending Study (0\%--30\%):} Conducted a parametric sweep of hydrogen blending ratios in natural gas (0\%--30\%) and compared flame characteristics and field distributions (temperature and major species).
\item \textbf{Emissions Assessment:} Evaluated the impact of hydrogen enrichment on emission characteristics, focusing on \textbf{NO$_x$} and \textbf{CO}, and summarized trends with supporting plots.
\item \textbf{Technical Reporting:} Delivered a structured thesis report documenting the modeling assumptions, numerical setup, comparative results, and key conclusions.
\end{rSubsection}

\end{rSection}

%--------------------------------------------------------------------------------------
%  Research Publications
%--------------------------------------------------------------------------------------
\begin{rSection}{Research Publications} \itemsep -3pt

\textbf{Yuqi HAN}, Co-author, \textit{Techno-economic Feasibility of Sustainable Aviation Fuel (SAF) Production in China} (EDF Internal Report; details available upon request). \hfill 2024\\
\textbf{Yuqi HAN}, \textit{Numerical Simulation Study on Premixed Hydrogen-Enriched Natural Gas Combustion} (Undergraduate Thesis, Northwestern Polytechnical University). \hfill 2023\\

\end{rSection}

%--------------------------------------------------------------------------------------
%  Awards
%--------------------------------------------------------------------------------------
\begin{rSection}{Awards} \itemsep -3pt

National Second Prize, 10th China College Student Competition on Marine Vessel Design and Production \hfill Jul 2021\\
National Second Prize, 14th China University Student Social Practice and Science \& Technology Competition on Energy Conservation and Emission Reduction \hfill Aug 2021\\
National Excellence Award, China University Student Innovation and Entrepreneurship Competition (RMB 20,000) \hfill May 2022\\
Outstanding Graduate, Northwestern Polytechnical University \hfill Jun 2023\\
France--Swiss Mobility Scholarship (EUR 3,000) \hfill Dec 2025\\

\end{rSection}

%--------------------------------------------------------------------------------------
%  Activities & Additional Information
%--------------------------------------------------------------------------------------
\begin{rSection}{Activities \& Additional Information}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{4ex}} p{0.78\textwidth} }
Language Skills &
English (C1); Chinese (Mandarin, Native); French (A2). \\

Driver's License &
China (valid; authorized for use in France); France (Permis B eligible). \\

Societies &
\textbf{Organization Committee Member, Youth League Committee of Northwestern Polytechnical University} --- Organized campus events and facilitated student engagement through collaboration with senior members. \\

&
\textbf{Member, International Leadership Program, United Nations Institute for Training and Research (UNITAR)} --- Engaged in global leadership and sustainable development initiatives through cross-cultural collaboration and project-based learning. \\

Volunteering &
Rural Agricultural Support Volunteer, China (2020); Global Power and Propulsion Society (GPPS) Volunteer (2021). \\
\end{tabular}

\end{rSection}

\end{document}
